\section{Custom User Controls}

This section describes Ingredient Auto Completion and Navigation Bar. Ingredient Auto Completion is the UserControl which lists the most relevant recipes when a user searches. The Navigation Bar section describes the navigation bar in the solution.

\subsection{Ingredient Auto Completion} \label{sec:AutoComplete}
Since it is only allowed to use ingredients which already exists in the database, there has to be a way of getting these ingredients when the user wants to add them in different situations.

The IngredientAutoComplete is a UserControl that searches through ingredients in the database, based on what a user types into a search field. It will then list the most relevant beneath the search field and allow the user to click one.

It exposes the DepencyProperties; MaximumItems and SelectItemCommand, which can be used to set how many items the list should display, and which command should be executed when the user selects an ingredient. This is set on the pages that uses this control.

When SearchText property changes, the control will try to repopulate the list of found ingredients. If a previous search with less letters came up with fewer ingredients than the maximum, the control will not attempt to query the database again, since that could not possibly give more results.

\subsection{Navigation Bar}\label{ssc:navBar}

As described in \cref{PagesLabel} the program contains different pages, and therefore navigation between these are needed. The program navigation is done through the black navigation bar which can be seen in \cref{fig:SettnigsPage}

The black navigation bar lets the user navigate between the five main pages of the solution, by clicking the icon of the wanted page once. When the user has clicked the icon, he is taken to the page using the Navigator class described in \cref{NavigatorLabel}