\subsection{Stories} \label{UserStories}
All products and processes of the design method springs from the product \textit{Stories}, which are shown below. The stories are written by different persons who have described their last shopping situation.
The stories vary in detail but can all be used to find different actions, requirements and problems, which is some of the aspects that are used in the following processes and products of the method.

\subsubsection{Person A}
\begin{quote}
I have invited guests for dinner Monday evening. We were having kale and ham, both something I had in the freezer, actually I had two hams in the freezer, because I bought one on a sale the day before, and that way I would be sure that there was enough meat, in this new and bigger ham. The only thing missing for the evening meal is now two litres of skimmed milk, so off I went to the grocery store, with my dog  on a leash. We walked to the closest store, which also happens to be a big store. When I entered the store, I began to doubt if the ham really was big enough, so I looked in the fridge with sausages.
I found a Christmas sausage on sale, and thought "Better safe than sorry" when I put the sausage in my basket, furthermore I thought to myself that any spare meat could be used as cold cuts, in the days to come. I headed for the two litres of milk, and then the checkout. On the way I passed the vegetable area, and saw dried figs, "Who can resist such a thing, so into the basket with those as well". I got through the checkout, and past the bakery on my way out to the dog, "The dog!", I could not forget to get her something, so I went back to the bakery to get a sausage roll. They had a sale, where you could buy 5 rolls, "So why not do so?".
\end{quote}

\subsubsection{Person B}
\begin{quote}
Last time I went shopping was when we in the household were to eat together. Another person in the household looked through the kitchen, to find out what was missing, and then told me; butter, potatoes, carbonated soft drinks, and dessert. I went to the closest store, and bought what was needed. When I returned to the apartment I decided that we should have the drink "White Russian" as desert, we had all we needed except milk, so off I went again, thinking that this extra trip could have been avoided if we had talked about which dessert I was actually meant to get, before I went for the first trip.
\end{quote}
 
\subsubsection{Person C}
\begin{quote}
Knowing that I want to shop the day after this day, I place a piece of paper on the table, and during the day, every time I remember basic stuff that we need, I write it down, things like, paper towels, rice, soap, and so forth. Later during the day I sit down to look through recipes to figure out what to have for dinner the next couple of days. I match recipes with what we already have at home, so that we can clear some of the storage, and in that way save some money, now that we are close to Christmas, and the budget therefore is a bit more tight, than normal. Because I based the meals on what we had at home, the shopping list did not get that long, therefore I was determined only to have to go to one store, the day after. Next day the planned shopping did not go as anticipated since both my husband and I had to work until late that day, therefore, I only went to get the most critical items on the shopping list, making an easy dinner for the evening, and food for the kids to bring as lunch the following day. During the shopping I remembered that my youngest child had to bring an advent present to school the next day, so I bought this as well and the rest of the shopping list had to wait until tomorrow.
\end{quote}

\subsubsection{Person D}
\begin{quote}
The last time I had to go shopping, was to get groceries for a Christmas party. My boyfriend and I had to get cabbage and cream to make kale, and we had to get marinated herring. Preferably we wanted to get herring marinated in tomatoes, and the cream had to be organic, because I am allergic to milk products that are not organic. Because of these requirements we chose to shop in one of the biggest malls, in the city. But to our big surprise, they did not have any marinated herring other than the ordinary, and they only had $1/4$ litre organic cream. Because of this this we therefore chose to get it in another store. Before we got to the checkout I found a Christmas gnome costume, for my niece, which I wanted to get for her, and to go with this costume we had to get a pair of matching tights as well. Furthermore my boyfriend found a cheap bathrobe, which he has wished for, for a long time and he therefore chose to buy it. We now went to the next store, to get the marinated herring and the half litre of cream that we are still missing. We found the cream, but we were still looking for the tomato marinaded herring. We did find some variations of marinade, but not any tomato marinade, which was our desired type. Never the less we chose to go with the another type of marinade, so we did not have to visit any more stores. On the way to the checkout, we also stumbled upon chocolate ideal for melting, which we were missing a few days before, when we wanted to make some Christmas candy, so we bought the items and went home.
\end{quote}

\subsubsection{Person E}
\begin{quote}
Last time I went shopping, I wrote to my girlfriend, over the internet, to see what was needed. Since she was at home she could quickly see this, and since I was at school I could easily  visit the grocery store on my way home. First we needed to figure out what to make for dinner. After dinner was decided my girlfriend quickly went through the kitchen to see what we needed. After she saw what was missing she texted me a list of missing items for dinner. When I was off school I texted my girlfriend to verify that we only needed the items she had texted me earlier. When I came to the grocery store, I started shopping after what was listed in the text message, and bought all the items, though a few items were sold out.  therefore I called home to inform that the needed items was sold out, and what item I needed to purchase instead. After the shopping was done I went home, only to find out that due to that I am the only one of us eating bacon, it was not put on the shopping list, and therefore I had to go out again to get the needed bacon.
\end{quote}

\subsubsection{Person F}
\begin{quote}
I live quite a long way from any shops and therefore I prefer to only shop once a week. And I prefer to only shop in one specific store. Due to the fact that I live long from the store, I do not return to the store, if I fond that I forgot something. During the week I note on a list what I need to get, so I do not have to walk around and remember it all the time. Before I note the items on the list I check to see if we have it in the freezer, garden or in the storage. So I do not get to much of something. Furthermore I look through recipes if I have to cook or bake something that I am not used to make.
\end{quote}

\subsubsection{Person G}
\begin{quote}
I rarely write down what I need to get, and therefore I mostly have to go shopping every day. Often I look through my inventory when I have to go shopping for something, to see if there is something else I am missing. Furthermore I normally plan what to buy when I know what kind of sales there are at the time. And if it is really good sales, I do not mind going to more than one shop. Lastly I often get so much from these sales, that I have to put some of it in the freezer, and in that way I have food for other days.
\end{quote}