\subsubsection{Technologies} \label{PACTech}
In the technology part of the PACT analysis, there is looked upon input, output and communication, which will be examined by the pros and cons of different relevant technologies, with a focus on tablet and smartphone related technologies.

\paragraph{Input}
The program should function as a planning tool, and include a shopping list, therefor the final platform will likely be tablets or smartphones, since they are more mobile than a laptop, and therefore there might not be any external plug-in devices that are going to be used for the solution. This means that the available input technologies are:
\begin{itemize}
    \item Cameras
    \item Microphones
    \item Touchscreens (includes multi-touch)
    \item Physical buttons
\end{itemize}

\emph{The camera,} can be used to input pictures, video or barcodes. Pictures and videos can be useful when the user adds content to the program, such as creating a recipe or adding a instructional videos. It is possible to get applications on some popular mobile operating systems such as iOS, Android and Windows Phone \cite{barcode_Phones}, that scan traditional barcodes and QR codes. Being able to read these codes could become useful if there are any relevant data on the 2D barcodes that needs to be transferred to the device. This data could be the item type or expiration date \cite{barcodeInc_FAQ}.           
    
\emph{The microphone,} can be used to input audio into the device. This can be useful if the users hands are occupied and they need to do some simple interaction with the program. These interactions would be made possible by the use of voice recognition software.

\emph{The touchscreen,} is easy to use and can be found in tablets and smartphones. The user can press the screen with their finger to interact with the program. Some touchscreens also enables the use of multi-touch technology, this enables more than one finger to be used when interacting with the touchscreen, this is often used for operations such as zooming (pinching) and rotating of pictures and text. This is useful in the general use of the program.

\emph{Physical buttons,} on the device could be used to navigate throughout the program, together with the standard functionality e.g. volume control. The amount of programmable buttons varies from device to device, the iPhone/iPad does not allow secondary functionality on their buttons. Some devices that run the Android OS allows for second functionality\cite{android_Rebind}, and can therefore be considered when designing the program.

\paragraph{Output}
The list of output technologies are:
\begin{itemize}
    \item Screen
    \item Speakers
    \item Vibration
\end{itemize}

\emph{The screen,} is used for visual display and visual feedback. Screen technology is useful to display large amount of information to the user.
The size of the screen must be taken into consideration when displaying information such as screen elements (e.g. buttons) and/or text.
Devices such as a laptop screen or desktop monitor can display many elements and large quantities of text, where as smartphones and tablets are restricted, both in resolution and dimensions. Large amounts of text can require pinching and scrolling making it hard to read. Also, large clutters or quantities of elements can be hard to navigate through. Lastly it can be useful for all screen sizes, to use ions to show what elements can do instead of using text, which can result in unnecessary use of screen space.

\emph{Speakers and/or vibration,} can be used in conjunction with the screen to give different kinds of feedback simultaneously.
Speakers and vibration are especially useful to give the user feedback in situations where the screen of the device is not visual. furthermore are the speakers helpful in situations were there are no physical contact with the device but it is still in hearing range. Vibration is useful when the user has physical contact with the device or in situations where sound might be hard to hear, or is disabled, this could be useful in crowded environments such as a shopping mall.     

\emph{Communication,} Communication covers how the solution is supposed to communicate with the internet and other users. The list of technologies used when using a smartphone or tablet, is:
\begin{itemize}
	\item Wi-Fi
	\item Telephone networks
    \item Database
\end{itemize}

\emph{Wi-Fi,} connection is a wireless connection to the internet.
This is a useful technology because all modern tablets and smartphones has Wi-Fi technology.
Wi-Fi can be used to synchronize data that is between devices, such as other smarthones or tablets, as well as an server

\emph{Telephone networks,} is used for the same reason as Wi-Fi. In order to use this sort of network to connect to the internet, most mobile companies, require the user to pay for this access, furthermore, some tablets are cheaper when they only provide Wi-Fi technology, but it comes in handy, in the way that you can connect to it almost every where, where as with Wi-Fi, you have to be in range of a provider.

\emph{A database,} can be used to store data on and the data can be accessed via the internet. This is useful because a database can store larger amounts of data than a mobile device. And it allows for easy access from multiple devises.
 
\paragraph{Conclusion}
Many different technologies are required to be considered when doing a PACT analysis, the technologies needed for the food planner application is from the three categories; input, output, and communication.
The technologies ranges from physical buttons, to Wi-Fi needed for the synchronization of the data. The chosen input technology that is going to be used is the touchscreen, as it is already widely used and works well with the solution. The chosen output technology is going to be screen display with a possibility  to include sound. The screen will show the necessary text and visual information, where the sound may be used for alerts or notifications. The communication technologies will going to be all of the previously described. Wi-Fi is useful for communicating with the server and other devices and the telephone networks can be used to transfer data when the user is outside of their home or work. The database will be used for holding a large amount of somewhat trivial data, such as the recipes. By having the recipes on the database the user saves room on their data storage device.