\subsection{Usability Test Tasks} \label{UsabilityAppendix}

When the test subjects of the usability test had been told how the test was conducted, they where given a list of taks that they had to perform within the program, to test the usability. These tasks are described underneath.

\textbf{Task 1}
You have nothing planned for tonight's meal, and you feel like having \textit{chicken and leek pie}.
\begin{itemize}
    \item Search for and add the \textit{chicken and leek pie} recipe for today’s meal
\end{itemize}

\textbf{Task 2}
On the way home from work, you want to do some shopping for tonight’s meal, but because you are on a bike, you cannot shop many items; therefore you want to change the number of days to shop for.
\begin{itemize}
    \item Navigate to the page that allows you to change number of days to shop for, and change this to 1.
\end{itemize}

\textbf{Task 3}
You have been doing some shopping for tonight’s \textit{chicken and leek pie} and want to add some bought items to your inventory
\begin{itemize}
    \item Find \textit{onion}, \textit{egg} and \textit{leek} on the shopping list and add them to the inventory list.
\end{itemize}

\textbf{Task 4}
You had a dinner planned with some friends, but due to bad planning from your friends, you have to cancel your plans.
\begin{itemize}
    \item Go to week 51, and remove \textit{Spinach and Cheese Souffle} from Monday the 15th of December.
\end{itemize}

\textbf{Task 5}
During the last shopping trip you also bought 5 \textit{lollipop sticks}. These have an expiration date that says \textit{16th of July 2017}.
\begin{itemize}
    \item Add 5 \text{lollipop sticks} to the inventory and change their expiration date to \textit{16th of July 2017}
\end{itemize}

\textbf{Task 6}
Friends have invited you over for a party Sunday the \textit{14th of December}, so you have to reschedule the meal you have planned for this day
\begin{itemize}
    \item Change the date of the meal on the \textit{14th of December} to be scheduled for a week later.
\end{itemize}

\textbf{Task 7}
After a long day, you feel like being good to yourself, you therefore eat some of the \textit{white chocolate} you have.
\begin{itemize}
    \item Remove \textit{100 ml} of \textit{white chocolate} from the inventory
\end{itemize}

\textbf{Task 8}
You have some friends over, when you decide to have some \textit{beer}
\begin{itemize}
    \item Remove all \textit{beer} from the inventory
\end{itemize}

\textbf{Task 9}
It is Christmas and you feel like having something with \textit{cinnamon} in it.
\begin{itemize}
    \item Search for recipes with \textit{cinnamon} and add one for today.
\end{itemize}

\textbf{Task 10}
You are having friends over for dinner \textit{Friday the 19th of December}; you know that you will be 9 persons in total
\begin{itemize}
    \item Find the recipe \textit{Hot and Smoky Cheeseburgers with Bacon and Pickled Cherry Pepper Relish} and add it for the \textit{19th of December}
    \item Change the number of meal participants to 9
\end{itemize}

\textbf{Task 11}
Because it is Christmas you decide that you want more recipes with \textit{cinnamon} to be shown.
\begin{itemize}
    \item Add \textit{cinnamon} to the list of rated ingredients with a rating of 100
\end{itemize}

\subsubsection{Follow-up questions}

After a test had been conducted, some follow-up questions were asked to find if the test participants had any comments about the usability of the program.

\begin{itemize}
    \item Do you have any general comments about the program?
    \item Did you find the program easy to use?
    \item Was the text easy to read, even though some of it were orange, and the background where grey?
    \item Did it make sense that the functionalities in the settings screen where placed there, or should they have been placed in other pages?
    \item Did the rate ingredients function make sense? Was 100 too many? Would 10 stars have been better?
    \item How did navigation work through the program? Was it easy to navigate through pages?
\end{itemize}