\section{Delimitation}

In this section the delimitation of the program is done. WHen the report was written and the sources were found, a lot of good ideas for the program was discussed. THese ideas were then written in the report, so to make the program, it was needed to delimit from some of the ideas, as the program might either become too complex or too time craving to make.

\subsection{Not in program}

In \cref{HowToAvoidFoodWaste} it is mentioned that incorporating leftovers is a good way to avoid food waste, according to The Danish Ministry of Environment. This is partially done in the program. In program, when the user makes a meal, the ingredients used will be taken away from the users inventory. If the user have leftover from the meal, they can add this to the inventory, and if these leftovers are needed to make some of the recipes incorporated in the program, these will then show up higher when planning meals.

in \cref{HowToAvoidFoodWaste} there is another initiative to reduce food waste, and that is by making stores available to sell quantity discount, but for the user to pick the items up at different times. This is not incorporated in the program, as this would require the project to have another focus than meal planning.

In \cref{HowToAvoidFoodWaste} another suggestion for reducing food waste is to inform the user of different methods to see if the food has gone bad. This is not done in the program. THe program does keep track of the expiration date of the items in the users inventory, but does not inform the user of different ways to see if the food has gone bad, as some of these dates might be guidance and not actual expiration of the food.

In the section \ref{HowToAvoidFoodWaste} it is also mentioned that if it where possible to share quantity discounts with other people, food waste would be reduced. This is not incorporated into the program because the focus of the report is on meal planning, and therefore it would require a complete shift of focus to make a program that was able to do this.

By keeping track of what is being thrown out, it can be seen if the same type of ingredients are being thrown out often, and the user might need to buy less of this ingredient it is suggested in \cref{HowToAvoidFoodWaste}. This is not in the program, as the program only tells the user to shop for the items needed for the recipes, and therefore the shopping list will only consist of needed items. 

It is mentioned in \cref{HowToAvoidFoodWaste} that by being creative with the leftovers, and making meals, from leftovers from what is already parts of a meal, food waste can be reduced. This is partially incorporated in the program, as the user can put in the leftovers in the inventory, and if a recipe uses these leftovers, recipes including these will be listed higher, when the user searches for a recipe to schedule, though there is not a specific initiative to use leftovers from meals creatively.



\subsection{In program}

In \cref{HowToAvoidFoodWaste} it is also suggested that by following recipes and using the exact amount of the ingredients will reduce the food waste. This has been incorporated into the program as a user has the ability to change how many people the recipe is for, and then the amount of the ingredients needed, also changes.

In \cref{HowToAvoidFoodWaste} it is also suggested using the items that expires soonest. This is part of the program, as the searching of adding a new recipe to the meal plan takes into consideration, and sorts the recipes so that the ones with ingredients expiring sooner gets higher up.