\section{Food waste}
Every year danish households throws away nearly 237.000 tons of food, that could have been eaten by people. This is estimated to be nearly 16 mio DKK. About 20 \% of a danish households foodbudget is wasted by throwing away food that could have been eaten, this means that if there was no food waste at all, 1 million people could be fed, this is nearly 1/5 of the danish people.

The people who throws away most food, are the people living alone. The average person living alone throws away 98.8 kg of food per year, where as a household with 5 people throws away 46.8 kg of food per person per year. It is mostly dairy products, vegetables and bread that gets thrown away, though in december a lot of meat is also thrown away, due to the fact that it is Christmas, where people eat more food.

Since 2007 the danish people have been purchasing 10 \% less food, a lot of this food used to end up in the trashcan as food waste. 54 \% of the danish people rarely or never uses the food from the night before for later eating, and 69 \% does not use leftovers for lunch the day after. Elderly people are better at using leftovers than younger people. \fxnote{references to bibliography, and/or maybe some graphs to show the numbers?}

20 \% of danish people does not make a grocery shopping list before going grocery shopping. 52 \% of people does not make a meal plan, 31 \% does sometimes and 17 \% does it often.

81 \% of danish people would use leftovers to avoid food waste, 50 percent would make a mealplan and make a grocery shopping list. 59 \% of the consumers believe that the danish food waste is their own fault.
