\section{Foodplan study}
\textit{Stop Spild Af Mad}\cite{madSpild_RapportAdfaerd} has conducted a study where eight informants had had to create and follow a weekly food-schedule.
Each participants had to create a foodplan and they could freely choose the different recipes with inspiration from cookbooks or the internet.

\subsection*{Planning}
The informants had some trouble with pulling them self together and getting started creating the foodplan, but they were happy to have it, once it was done. It could be beneficial for the person that were in charge of grocery-shopping, to be the one making the schedule, since the involvement of other members from the family could increase the time of making it.

\subsection*{Modules}
It was almost impossible for the informants to follow the schedule for a whole week, without having to reorganize or modify it. Most of the informants made small modules, that could be moved around depending on the family's situation. It was optimal with modules spanning two-three days. Varied meals was preferred, and not simply reheated meals.

\subsection*{grocery-shopping}
Seven out of the eight participants was shopping groceries almost every day. This was not seen as a nuisance, but after having planned grocery-shopping for a whole week, they experienced a big relief in their everyday life. This was expressed in terms of more personal freedom as a consequence of saving time and money. Planning ahead also decreased buying on impulse.
\fxnote{textbf might be a bad choice.. CHS tried using emphasize on Less gro... and subsubsec on Modules (subsubsec throws a warning because we have no subsec beforehand .. please evaluate, on which type we should use.}

\subsection{Reflection} \fxnote{This is some sort of conclusion/reflection for this section, but might need to be moved.}
The participant had trouble getting started creating a new food plan for the week. They also wanted a more realistic food-schedule instead of having to create it from cookbooks. Realistic in the sense that the plan should fit into their context. A solution to this problem might be solved by automating a lot of the tasks involved with having to come up with the different recipes and do the grocery shopping.
By having an application come up with suggested meals based on different aspects such as the:
\begin{itemize}
\item Food you already have
\item Food you like
\item Price
\item Stock of stores nearby
\end{itemize}
People could quickly create the schedule or maybe even have the application create it for them.