\subsection{Interview answers}
\subsubsection{25 year old single\fxnote{What should we call these?}}
\begin{itemize}
  \item[Sex] Male
  \item[Age] 25
  \item[Education] Vocational\fxnote{use this word for 'erhvervsuddannelse'?}
  \item[Work] Skilled Sailor
  \item[Household] 3 singles
\end{itemize}
\emph{What do you characterize as foodwaste, and is it a problem in the household?}

If any kind of food is thrown out, it is foodwaste according to the participant, furthermore he thinks foodwaste is a problem in the household, he elaborates that he thinks it is because some food is sold in bundles, that are to big compared with what is needed, and that they therefore buy to much food.

\emph{Is there a difference in the type of food, that is thrown out?}

It is mostly vegetables, which is thrown out in the household

\emph{What factor is in focus, when food is thrown out?}

The participant only look at the freshness of the food, and does not take best before date in account.

\emph{Planning meals and shopping}

The participant does rarely plan more then one day ahead, and does not plan at any specific time in the day. Furthermore the participant mostly shop for what is wanted the specific day, and it is rarely considered, if a meal could be made, from what is in the home. No one specific in the household do the shopping or the cooking, but they try to schedule the shopping with who has the time, or already has to be out.

\emph{What is the most important about your diet?}

Quality is the most important, closely followed by organic food, they try to avoid foodwaste, but it is not in focus.

\emph{Do you use leftovers?}

The participant always use leftovers, both because he finds it stupid, to throw it out, but also to save some money.
\paragraph{Shopping}
\emph{When do you shop, for how long, how much and how many times?}

Preferably in the morning, because there are less people. The shopping only takes 5-10 minutes and is done 4 - 5 times a week. Breakfast and lunch is often bought for a few days, where the dinner is mostly bought on the day.

\emph{What affects you in the shopping situation?}

Is not affected by sales in general, but do impulsive shopping if groceries are on sale, because they are close to the best before date.