\chapter{System Choice}
In this chapter the three sub activities \textit{Situation, Ideas and System definition} when defining the system, will be described. To describe the system choice we will be using systems development where system choice will be described this way situation, ideas and systems.

\section{Situation} \label{SituationLabel}
\input{Analysis/RichPicture}

\section{Ideas} \label{IdeasLabel}
\input{Analysis/Exemplars}

\section{System}
This section formulates the system definition. This is done by first writing a FACTOR criteria and then using this to formulate the system definition. The system definition is a description of a computerized system in a natural language. The system definition is used to describe the characteristics of a system.
\subsection{Definition (FACTOR)}
To formulate a system definition we used the FACTOR \cite{OOAD_BATOF} criteria to establish important parts of the system.

\begin{description}
	\item[Functionality] Help users organize a meal plan based on their preferences and inventory. Create/edit user, inventory and plan.
	\item[Application domain] System maintenance staff, Users planning meals.
	\item[Conditions] The system will be used by users with varying technical abilities and cooking experience.
	\item[Technology] Tablet, smartphone
	\item[Objects] Family member (user), inventory (groceries), recipe
	\item[Responsibility] An administrative/planning tool
\end{description}

\subsection{System Definition}
A system which primarily lets you plan your meals in advance based on what is in your inventory to assist the user and reduce food waste.
Secondarily the program will allow administration of a meal plan and inventory and incorporate functions to alter this plan and inventory by adding or removing recipes and groceries. The system maintenance staff will make sure that the system is operating correctly.
The system will be designed for tablets and smartphones, as these devices offers mobility and thereby available both in and out of the user's home.